Understanding the Ratings of Children's Books: A Data-Driven Analysis

### 2024-12-15 paper.qmd
paper
improved paper

We use the statistical programming language R [@R] to generate, clean, and analyze the dataset. Our data, sourced from the children's book ratings dataset hosted on GitHub by Timothy A. Cookson [@dataset], includes metadata for 3,769 children’s books. The dataset contains information like International Standard Book Number, title, author, cover type, pages, and rating, which form the basis for our analysis. Children's book ratings offer insights into reader preferences, guiding publishers and authors in producing appealing literature. This dataset provides a valuable lens into these preferences through user-generated ratings. We focus on attributes that may influence book ratings, such as the type of cover, number of pages, and the original year of publishing.

@@

@tbl-regression-results summarizes the regression results, showing the estimated coefficients, median absolute deviations, and credible intervals for each predictor.
```{r}
#| label: tbl-regression-results
#| echo: false
#| tbl-cap: "Regression model summary showing that hardcover books and those with 150-299 pages are positively associated with higher ratings, while books published before 2000 tend to receive lower ratings. Credible intervals confirm that these associations are statistically significant."
#| warning: false
#| message: false

@@

Another convergence diagnostic involves examining trace plots. Trace plots show the sampled values of each parameter across iterations for each Markov chain. Well-mixed chains with no clear trends suggest that the model has converged. In @fig-trace-plot , we observe the trace plots for key parameters in the model.

```{r}
#| label: fig-trace-plot
#| echo: false
#| fig-cap: "Trace plots for key parameters across the Markov chains, showing well-mixed chains with stable values. The lack of discernible patterns or trends confirms that convergence has been reached."
#| fig-width: 10 
#| fig-height: 7 
#| dpi: 300

@@

Posterior predictive checks are used to assess the goodness-of-fit of the Bayesian model. By simulating data from the posterior distribution, we can compare the simulated data to the observed data to determine if the model adequately represents the data. @fig-posterior-checks illustrates the results of posterior predictive checks for the Bayesian model.

```{r}
#| label: fig-posterior-checks
#| echo: false
#| fig-cap: "Posterior predictive checks showing a comparison between the observed data and simulated data generated from the model's posterior distribution. This helps evaluate whether the model adequately captures the key features of the observed data."

>>>>

We use the statistical programming language R [@R] to generate, clean, and analyze the dataset. Our data, sourced from the children's book ratings dataset hosted on GitHub by Timothy A. Cookson [@dataset], includes metadata for 9,240 children's books. After cleaning, 3,769 children’s books are used to analyze. The dataset contains information like International Standard Book Number, title, author, cover type, pages, and rating, which form the basis for our analysis. Children's book ratings offer insights into reader preferences, guiding publishers and authors in producing appealing literature. This dataset provides a valuable lens into these preferences through user-generated ratings. We focus on attributes that may influence book ratings, such as the type of cover, number of pages, and the original year of publishing.

@@

@tbl-regression-results summarizes the regression results, showing the estimated coefficients, median absolute deviations, and credible intervals for each predictor. Credible intervals confirm that these associations are statistically significant.
```{r}
#| label: tbl-regression-results
#| echo: false
#| tbl-cap: "Regression model summary showing that hardcover books and those with 150-299 pages are positively associated with higher ratings, while books published before 2000 tend to receive lower ratings."
#| warning: false
#| message: false

@@

Another convergence diagnostic involves examining trace plots. Trace plots show the sampled values of each parameter across iterations for each Markov chain. Well-mixed chains with no clear trends suggest that the model has converged. In @fig-trace-plot, we observe the trace plots for key parameters in the model. The lack of discernible patterns or trends confirms that convergence has been reached.

```{r}
#| label: fig-trace-plot
#| echo: false
#| fig-cap: "Trace plots for key parameters across the Markov chains, showing well-mixed chains with stable values."
#| fig-width: 10 
#| fig-height: 7 
#| dpi: 300

@@

Posterior predictive checks are used to assess the goodness-of-fit of the Bayesian model. By simulating data from the posterior distribution, we can compare the simulated data to the observed data to determine if the model adequately represents the data. @fig-posterior-checks illustrates the results of posterior predictive checks for the Bayesian model. This helps evaluate whether the model adequately captures the key features of the observed data.

```{r}
#| label: fig-posterior-checks
#| echo: false
#| fig-cap: "Posterior predictive checks showing a comparison between the observed data and simulated data generated from the model's posterior distribution."
